---
title: "Report"
author:
- familyname: Wang
  othernames: Yiru
  address: Monash Universtidy
  email: "ywan0553@student.monash.edu"
  correspondingauthor: true
  qualifications: section1
- familyname: Xu
  othernames: Kexin
  address: Monash University
  email: "kxuu0029@student.monash.edu"
  qualifications: section2
  correspondingauthor: true
- familyname: Tang
  othernames: Ruiqi
  address: Monash University
  email: "rtan00062student.monash.edu"
  correspondingauthor: true
  qualifications: section3
department: Our consultancy \newline Yiru Wang &\newline Kexin XU &\newline Ruiqi Tang
organization: Australian Government COVID19
bibliography: references.bib
biblio-style: authoryear-comp
linestretch: 1.5
always_allow_html: true
output:
  bookdown::pdf_document2:
    template: monashreport2.tex
    fig_caption: yes
    includes:
      in_header: preamble.tex
    keep_tex: yes
    number_sections: yes
    citation_package: biblatex
    toc: false
header-includes:
 \usepackage{float}
 \floatplacement{figure}{H}
 \floatplacement{table}{H}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, 
                      eval = TRUE,
                      cache=TRUE, 
                      messages=FALSE, 
                      warning=FALSE)
```



```{r, echo = FALSE, message = FALSE, warning = FALSE}
# Libraries
library(tinytex)
library(gridExtra)
library(tidyverse)
library(readr)
library(bookdown)
library(knitr)
library(plotly)
library(kableExtra)
```

\clearpage

\section*{State}


\clearpage

\section*{Gender}

```{r echo=FALSE, message = FALSE, warning = FALSE}
Victims_of_Crime_raw <- readxl::read_excel("data/Victims_of_Crime_Australia.xls", sheet = 3, skip = 4, col_names = FALSE)
Victims_of_Crime <- Victims_of_Crime_raw[-1,1:11]
colnames(Victims_of_Crime) = Victims_of_Crime[1,]
Victims_of_Crime <- Victims_of_Crime[-1,]
Homicide <- Victims_of_Crime[-1,] %>% 
  slice(c(1:18)) %>% 
  filter(`Sex and age` == "Total")
Homicide[1,1] <- "Homicide_Male"
Homicide[2,1] <- "Homicide_Female"
Homicide[3,1] <- "Homicide_All"
Homicide <- Homicide %>% rename("Type_Gender" = `Sex and age`)
Murder <- Victims_of_Crime %>% 
  slice(c(21:38)) %>% 
  filter(`Sex and age` == "Total")
Murder[1,1] <- "Murder_Male"
Murder[2,1] <- "Murder_Female"
Murder[3,1] <- "Murder_All"
Murder <- Murder %>% rename("Type_Gender" = `Sex and age`)
Attemptedmurder <- Victims_of_Crime %>% 
  slice(c(40:57)) %>% 
  filter(`Sex and age` == "Total")
Attemptedmurder[1,1] <- "Attemptedmurder_Male"
Attemptedmurder[2,1] <- "Attemptedmurder_Female"
Attemptedmurder[3,1] <- "Attemptedmurder_All"
Attemptedmurder <- Attemptedmurder %>% rename("Type_Gender" = `Sex and age`)
Manslaughter <- Victims_of_Crime %>% 
  slice(c(59:76)) %>% 
  filter(`Sex and age` == "Total")
Manslaughter[1,1] <- "Manslaughter_Male"
Manslaughter[2,1] <- "Manslaughter_Female"
Manslaughter[3,1] <- "Manslaughter_All"
Manslaughter <- Manslaughter %>% rename("Type_Gender" = `Sex and age`)
Sexualassault <- Victims_of_Crime %>% 
  slice(c(78:110)) %>% 
  filter(`Sex and age` == "Total")
Sexualassault[1,1] <- "Sexualassault_Male"
Sexualassault[2,1] <- "Sexualassault_Female"
Sexualassault[3,1] <- "Sexualassault_All"
Sexualassault <- Sexualassault %>% rename("Type_Gender" = `Sex and age`)
Kidnappingabduction <- Victims_of_Crime %>% 
  slice(c(112:141)) %>% 
  filter(`Sex and age` == "Total")
Kidnappingabduction[1,1] <- "Kidnappingabduction_Male"
Kidnappingabduction[2,1] <- "Kidnappingabduction_Female"
Kidnappingabduction[3,1] <- "Kidnappingabduction_All"
Kidnappingabduction <- Kidnappingabduction %>% rename("Type_Gender" = `Sex and age`)
Robbery <- Victims_of_Crime %>% 
  slice(c(143:175)) %>% 
  filter(`Sex and age` == "Total")
Robbery[1,1] <- "Robbery_Male"
Robbery[2,1] <- "Robbery_Female"
Robbery[3,1] <- "Robbery_All"
Robbery <- Robbery %>% rename("Type_Gender" = `Sex and age`)
Armedrobbery <- Victims_of_Crime %>% 
  slice(c(177:209)) %>% 
  filter(`Sex and age` == "Total")
Armedrobbery[1,1] <- "Armedrobbery_Male"
Armedrobbery[2,1] <- "Armedrobbery_Female"
Armedrobbery[3,1] <- "Armedrobbery_All"
Armedrobbery <- Armedrobbery %>% rename("Type_Gender" = `Sex and age`)
Unarmedrobbery <- Victims_of_Crime %>% 
  slice(c(211:243)) %>% 
  filter(`Sex and age` == "Total")
Unarmedrobbery[1,1] <- "Unarmedrobbery_Male"
Unarmedrobbery[2,1] <- "Unarmedrobbery_Female"
Unarmedrobbery[3,1] <- "Unarmedrobbery_All"
Unarmedrobbery <- Unarmedrobbery %>% rename("Type_Gender" = `Sex and age`)
Blackmailextortion <- Victims_of_Crime %>% 
  slice(c(245:274)) %>% 
  filter(`Sex and age` == "Total")
Blackmailextortion[1,1] <- "Blackmailextortion_Male"
Blackmailextortion[2,1] <- "Blackmailextortion_Female"
Blackmailextortion[3,1] <- "Blackmailextortion_All"
Blackmailextortion <- Blackmailextortion %>% rename("Type_Gender" = `Sex and age`)
Victims_of_Crime_tidy <- bind_rows(Homicide, Murder, Attemptedmurder, Manslaughter, Sexualassault, Kidnappingabduction, Robbery, Armedrobbery, Unarmedrobbery, Blackmailextortion) %>% 
  mutate(`2010` = as.numeric(`2010`)) %>% 
  pivot_longer(cols = -Type_Gender, 
               names_to = "Year",
               values_to = "Number") %>% 
  separate(col = Type_Gender,
           into = c("Type", "Gender"), "_") %>% 
  filter(!Type == "Homicide",
         !Type == "Robbery")
```

```{r echo=FALSE, fig.height=10, fig.width=11, message = FALSE, warning = FALSE}
g <- Victims_of_Crime_tidy %>% 
  group_by(Year, Gender) %>%
  summarise(sum = sum(Number)) %>% 
  ggplot(aes(x = Year,
             y = sum,
             color = Gender,
             group = Gender)) +
  geom_line() +
  theme_bw()
g
#ggplotly(g)
```

* On the whole, it shows an upward trend year by year recently.  
* The number of female victims is much higher than that of male victims, almost twice.


```{r echo=FALSE, message = FALSE, warning = FALSE}
Victims_of_Crime_tidy %>% 
  ggplot() +
  geom_col(aes(x = Year,
                y = Number,
                fill = Gender),
           position = "dodge") +
  facet_grid(Type~., scales = "free_y") +
  scale_fill_brewer(palette = "Dark2") +
  theme_bw()
```

* With the exception of sexual assault and kidnapping, the majority of victims are men.
* The vast majority of cases are sexual assaults.  
* The number of robberies among the remaining crime categories is also considerable. (Including both armed and unarmed)  
* Possible reasons:
  + Women generally have stronger safety awareness
  + Women are less likely to be seen alone at night in areas where they are likely to be robbed  
    
According to statistics of gender-specific crimes in various countries, male victims are the majority in almost all crimes except for sex-related crimes in which more women are victims.





```{r echo=FALSE, message = FALSE, warning = FALSE}
Victims_of_Crime_sum <- Victims_of_Crime_tidy %>% 
  filter(!Gender == "All") %>% 
  group_by(Gender, Year) %>% 
  summarise(sum = sum(Number))

Victims_of_Crime_tidy %>% 
  filter(Type == "Sexualassault" &
         !Gender == "All") %>% 
  left_join(Victims_of_Crime_sum) %>% 
  group_by(Gender, Year) %>% 
  summarise(sa_rate = Number/sum*100) %>% 
  kable(caption = "Sexual Assault Rate") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))
```

Take sexual assault, female victims of sexual assault make up a very high proportion of total female victims.  


```{r echo=FALSE, message = FALSE, warning = FALSE}
Victims_of_Crime1 <- Victims_of_Crime_raw[-1,c(1, 12:21)]
colnames(Victims_of_Crime1) = Victims_of_Crime1[1,]
Victims_of_Crime1 <- Victims_of_Crime1[-1,]

Sexualassault1 <- Victims_of_Crime1 %>% 
  slice(c(78:110)) %>% 
  filter(`Sex and age` == "Total")
Sexualassault1[1,1] <- "Sexualassault_Male"
Sexualassault1[2,1] <- "Sexualassault_Female"
Sexualassault1[3,1] <- "Sexualassault_All"
Sexualassault1 <- Sexualassault1 %>% rename("Type_Gender" = `Sex and age`)

Sexualassault_rate <- Sexualassault1 %>% 
  mutate(`2010` = as.numeric(`2010`)) %>% 
  pivot_longer(cols = -Type_Gender, 
               names_to = "Year",
               values_to = "Rate") %>% 
  separate(col = Type_Gender,
           into = c("Type", "Gender"), "_") %>% 
  filter(!Gender == "All")
```




```{r echo=FALSE, message = FALSE, warning = FALSE}
sa <- Sexualassault_rate %>%
  ggplot() +
  geom_col(aes(x = Year,
               y = Rate,
               fill = Gender),
               position = "dodge") +
  theme_bw() +
  scale_fill_brewer(palette = "Dark2") + 
  theme(legend.position = "bottom")
sa
#ggplotly(sa)
```

* Rate is calculated by victim number divided by 100,000 persons.
* Show an upward pattern over years.
* Higher than 0.15% in recent years which means 3 out of every 2,000 people have been sexually assaulted.
* Possible reasons:
  + Women are physically vulnerable
  + Men are more sexually impulsive
  + Many women may choose not to report the crime
    - relationship to the offender
    - confidence in the justice system
    - fear of revenge
    - public opinion  
  
ABS personal safety survey also measures the number of women who contacted the police about the most recent incident within the last 10 years. Only 13.4% of women did so. 



\clearpage

\section*{Age}


